Software Citation Principles

### 2016-02-17 sc-principles/software-citation-principles.tex
Mostly notes describing areas to highlight

>>>>

With close to 50 working group partipants representing a range of research domains, the working group was tasked to
document existing practices in their respective communities. A total of 47 documents were submitted by working group
participants with the life sciences, astrophysics and geosciences being particularly well-represented in the submitted
resources.

\textbf{Breakdown of resources}

NOTE: Should mention that a number of communities have already focussed their attention on issues around data citation and while
this isn't exactly the same there are many similarities (what is different exactly?).

\textbf{General community/non domain-specific efforts}

Some of the most actionable work has come from the SSI in the form of blog posts written by their community fellows:

In a blog post from 2012, \cite{ssi-how-to-cite} discussing some of the pitfalls of trying to cite software in publications.
The author includes useful guidance for when to consider citing software as well as some ways to help `convince' journal editors
to allow the inclusion of software citations.

In \cite{ssi-citation-files}, Wilson suggests that software authors include a `CITATION' file that documents exactly how the
authors of the software would like to be cited by others. While this isn't a formal metadata specification (it's not machine
readable for example) this does offer a solution for authors wishing to give explicit instructions to potential citing authors.
In a later post on the SSI blog, Jackson \cite{ssi-how-shalt-i-cite-thee} gives a good overview of some of the approaches
package authors have taken to automate the generation of citation entities such as bibtex entries.

NSF/NIH workshops. WSSSPE. JISC reports.

\textbf{Domain-specific community activities}

Astronomy: ASCL, AAS journals announcing they will accept software papers in their journals \cite{aas-sofware-papers}. AAS/GitHub
workshop \cite{aas-software-index} dedicated to software citation, indexing and discoverability.

....lots more to add here.

\textbf{Existing principles}

Author guidelines in F1000Research, APA authors, SSI `publish or be damned' \cite{ssi-publish-or-be-damned} manifesto.

\textbf{Existing efforts around metadata standards}

AAS workshop (\cite{aas-software-index}), CRediT project \cite{casrai-credit}, others...

\textbf{Studies of author motivations}

Survey of data citation practices \cite{Kratz_2015}
